The Place of the Local Group in the Cosmic Web

### 2014-04-24 paper/main.tex
updated figures

\title{The Local Group in the Cosmic Web} 
\author{
  XXXX\altaffilmark{1},
  YYYY\altaffilmark{2},
  ZZZZ\altaffilmark{3}
}

@@

%lg rare
The configuration of galaxies in the Local Group (LG hereafter) is quite rare to find in the local Universe and in cosmological simulations. 
The LG is dominated by the two big spirals MW and M31, the next most-luminous galaxy is M33 which is $\sim 10$ times less massive than M31, followed by several less luminous dwarf galaxies, up to a distance of $\sim 3$\mpc.
The velocity vector of M31, with a low tangential velocity is consistent to a head-on collision orbit toward the MW \citep{2008MNRAS.386..461C,2012ApJ...753....8V,2012ApJ...753....7S}.
Another feature of the Local group is the relatively low velocity dispersion of nearby galaxies up to $\sim 8$ Mpc \citep[][and references therein]{1975ApJ...196..313S,2011MNRAS.415L..16A}.
Environment around the Local Group has density quite
close to the average density of the universe \citep{2003ApJ...596...19K,2005AJ....129..178K}. In addition, the closest massive galaxy cluster, the Virgo Cluster, is $\approx 16.5\ \mpc$ away \citep{2007ApJ...655..144M}.

All this combination of features make LG analogues very rare to find. Using numerical simulatons \citet{lganalogues} found less than $2\%$ MW-sized halos reside in a pair similar to MW-M31 and in a similar environment. Furthermore, if we select pairs constrained within $2\sigma$ error fron current observational measurements of the velocity components and distance to M31, there are only $88$ systems in a cube of $250$ \hmpc side.
\citet{2013ApJ...767L...5F} also study MW-M31 pairs in numerical simulations finding the typical quantities characterizing the orbital parameters of the LG are rare among typical pairs, but not enough to challenge the \lcdm model.
Another definition of LG analogues is made by \citet{2008MNRAS.384.1459L}, but despite differences ocurr in the definitions and resulting fraction of LG analogues, all are in agreement with a low frequency of these pairs.
%lw08 also look lg analogues

%larger scales & lg env
To understand better the properties of the LG and how this uncommon pair configuration fit in the cosmological context, an immediate question arise. What else can we say of the LG at larger scales?. In particular, which are the typical/prefered locations of these systems within the Cosmic Web?.
Looking the LG at larger scales we have it is located in a difuse and warped filament/wall conecting Virgo Cluster with Fornax Cluster, some nearby galaxies and groups members of this large structure are the Maffei group, NGC $6744$, NGC $5128$, $M101$, $M81$, $NGC1023$, Cen A group. At this scale, there is no evident alignment of the MW-M31 orbital plane with the local filament or the Virgo-Fornax direction. 
However, if we look in a smaller volume below scales of $\sim 6$ \mpc, there is a clear alignment of th the MW-M31 orbit with a local plane as shown by figure $3$ in \citet{2013AJ....146...69C}.

@@

The fractional anisotropy (FA) \citep{Libeskind2013} is a quantity
that measures the relative strength of the three eigenvalues and
therefore can be interpreted as the relative strenght of
compression/tension exterted by the tidal field. It is defined as:

\begin{equation}
{\mathrm FA}=\frac{1}{\sqrt{3}}\sqrt{\frac{(\lambda_1- \lambda_3)^2 + (\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{\lambda_1^2+\lambda_2^2 + \lambda_3^2}}.
\end{equation}
%
An additional advantage of the FA is that it does not depend on the
choice of $\lambda_{\rm th}$ and can be used as a broad gauge of the
kinds of tidal forces on the Local Group.

@@

To construct a sample of the MW-M31 pairs at $z\approx 0$, we use a series of simulation snapshots  at $z<0.1$ (i.e. in the last $\approx 1.3$ Gyr before present) spaced by $\approx 150-250$ Myr. This is done because a particular configuration of MW and M31 is transient and would correspond to a relatively small number of systems at one snapshot. By using multiple snapshots we can increase the sample of systems in such configuration during a period of time in which secular cosmological evolution is small.
Pairs are selected allowing a wide range of masses, following an isolation critera, constraining by orbital measurements such as radial, tangential velocity and separation of the pair, and local environment constrains such as local velocity dispersion and local overdensity within a sphere of radius $5$ \mpc. A full description of the selection criteria can be found in \citet{lganalogues,sat}.

@@

The first results we explore is the kind of environment occupied by
our LGs. We find that LGs in the restricted $2\sigma$ and $3\sigma$
samples prefer by large to be in filaments and sheets. Almost $\sim 50\%$ of the
pairs in both cases can be found in filaments while $\sim 40\%$ can be
found in sheets. This proportion is in stark contrast to the
environments for the general pair sample. In that case only $\sim
27\%$ and $\sim 33\%$ can be found in filaments and sheets,
repectively. There is a considerable fraction of pairs that are
located in peaks ($\sim 25\%$) and voids ($\sim 15\%$). These results
and the exact numbers are presented in Table \ref{table:web_type}.

@@

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.45\textwidth]{density_histogram.eps}
\end{center}
\caption{Overdensity distribution for the pairs in the three samples.
    \label{fig:density}}  
\end{figure}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.45\textwidth]{FA_histogram.eps}
\end{center}
\caption{Integrated Fractional Anisotropy distribution for the pairs
  in the three samples. 
    \label{fig:FA}}  
\end{figure}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.45\textwidth]{FA_delta_scatter.eps}
\end{center}
\caption{Density and Fractional Anisotropy distribution for the pairs
  in the general and $3\sigma$ samples. 
    \label{fig:delta_FA}}  
\end{figure}

@@

>>>>

\title{The Place of the Local Group in the Cosmic Web} 
\author{
  XXXX\altaffilmark{1},
  YYYY\altaffilmark{2},
  ZZZZ\altaffilmark{3}
}

@@

%lg rare
The configuration of galaxies in the Local Group (LG hereafter) is quite rare to find in the local Universe and in cosmological simulations. 
The LG is dominated by the two big spirals MW and M31, the next most-luminous galaxy is M33 which is $\sim 10$ times less massive than M31, followed by several less luminous dwarf galaxies, up to a distance of $\sim 3$\mpc.
The velocity vector of M31, with a low tangential velocity is
consistent to a head-on collision orbit toward the MW
\citep{2008MNRAS.386..461C,2012ApJ...753....8V,2012ApJ...753....7S}.

Another feature of the Local group is the relatively low velocity
dispersion of nearby galaxies up to $\sim 8$ Mpc \citep[][and
  references therein]{1975ApJ...196..313S,2011MNRAS.415L..16A}. 
Environment around the Local Group has density quite close to the
average density of the universe
\citep{2003ApJ...596...19K,2005AJ....129..178K}. In addition, the
closest massive galaxy cluster, the Virgo Cluster, is $\approx
16.5\ \mpc$ away \citep{2007ApJ...655..144M}.

All this combination of features make LG analogues very rare to
find. Using numerical simulatons \citet{lganalogues} found less than
$2\%$ MW-sized halos reside in a pair similar to MW-M31 and in a
similar environment. Furthermore, if we select pairs constrained
within $2\sigma$ error fron current observational measurements of the
velocity components and distance to M31, there are only $88$ systems
in a cube of $250$ \hmpc side.

\citet{2013ApJ...767L...5F} also study MW-M31 pairs in numerical
simulations finding the typical quantities characterizing the orbital
parameters of the LG are rare among typical pairs, but not enough to
challenge the \lcdm model. 
Another definition of LG analogues is made by
\citet{2008MNRAS.384.1459L}, but despite differences ocurr in the
definitions and resulting fraction of LG analogues, all are in
agreement with a low frequency of these pairs. 
%lw08 also look lg analogues

%larger scales & lg env
To understand better the properties of the LG and how this uncommon
pair configuration fit in the cosmological context, an immediate
question arise. What else can we say of the LG at larger scales?. In
particular, which are the typical/prefered locations of these systems
within the Cosmic Web?.

Looking the LG at larger scales we have it is located in a difuse and
warped filament/wall conecting Virgo Cluster with Fornax Cluster, some
nearby galaxies and groups members of this large structure are the
Maffei group, NGC $6744$, NGC $5128$, $M101$, $M81$, $NGC1023$, Cen A
group. At this scale, there is no evident alignment of the MW-M31
orbital plane with the local filament or the Virgo-Fornax direction.

However, if we look in a smaller volume below scales of $\sim 6$ \mpc,
there is a clear alignment of th the MW-M31 orbit with a local plane
as shown by figure $3$ in \citet{2013AJ....146...69C}.

@@

The ellipticity and the prolatenes are quantities that measure the
relative strength of the three eigenvalues. They are defined as
follows

\begin{equation}
e= \frac{\lambda_3 - \lambda_1}{2(\lambda_1 + \lambda_2 + \lambda_3)}, 
\end{equation}

\begin{equation}
p= \frac{\lambda_1 + \lambda_3 - 2\lambda_2}{2(\lambda_1 + \lambda_2 +
  \lambda_3)}.
\end{equation}

@@

To construct a sample of the MW-M31 pairs at $z\approx 0$, we use a
series of simulation snapshots  at $z<0.1$ (i.e. in the last $\approx
1.3$ Gyr before present) spaced by $\approx 150-250$ Myr. This is done
because a particular configuration of MW and M31 is transient and
would correspond to a relatively small number of systems at one
snapshot. By using multiple snapshots we can increase the sample of
systems in such configuration during a period of time in which secular
cosmological evolution is small.

Pairs are selected allowing a wide range of masses, following an
isolation critera, constraining by orbital measurements such as
radial, tangential velocity and separation of the pair, and local
environment constrains such as local velocity dispersion and local
overdensity within a sphere of radius $5$ \mpc. A full description of
the selection criteria can be found in \citet{lganalogues,sat}.

@@

\subsection{Pairs in Filaments and Sheets}

The first result we explore is the kind of environment occupied by
our LGs. We find that LGs in the restricted $2\sigma$ and $3\sigma$
samples prefer by large to be in filaments and sheets. Almost $\sim 50\%$ of the
pairs in both cases can be found in filaments while $\sim 40\%$ can be
found in sheets. This proportion is in stark contrast to the
environments for the general pair sample. In that case only $\sim
27\%$ and $\sim 33\%$ can be found in filaments and sheets,
repectively. There is a considerable fraction of pairs that are
located in peaks ($\sim 25\%$) and voids ($\sim 15\%$). These results
and the exact numbers are presented in Table \ref{table:web_type}.

@@

\subsection{Overdensity, Ellipticity and Anisotropy}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{density_histogram.pdf}
\end{center}
\caption{Overdensity distribution for the pairs in the three samples.
    \label{fig:density}}  
\end{figure}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.49\textwidth]{ELL_histogram.pdf}
  \includegraphics[width=0.49\textwidth]{PROL_histogram.pdf}
\end{center}
\caption{Cumulative distributions for the ellipticity and prolateness.
    \label{fig:ELL_PROL}}  
\end{figure*}

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.49\textwidth]{ELL_delta_scatter.pdf}
  \includegraphics[width=0.49\textwidth]{PROL_delta_scatter.pdf}
\end{center}
\caption{Ellipticity and prolateness versus the overdensity for the pairs
  in the general and $3\sigma$ samples.  \label{fig:delta_ELL_PROL}}  
\end{figure*}

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{alignments_e3.pdf} 
\end{center}
\caption{Cumulative distributions for the alignment between the normal
  vector $\hat{n}$ and the third eigenvector $\vec{e}_3$.
    \label{fig:alignment}}  
\end{figure}

@@

\subsection{Alignment along the cosmic web}
